How to Analyze Build Logs --- A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-24 tse-paper/content.tex
Fix left-over comments

%% \begin{itemize}
%%   \item \textbf{(referred to as PBE)}
%%   Based on manually supplied example pairs of build logs and chunks,
%%   PBE automatically synthesizes
%%   a regular expression extracting the given chunks within the build logs.
%%   % these second sentences about what the techniques stand for could
%%   % also be merged to a paragraph after the itemize
%%   PBE mimics regular expressions and parsers while
%%   simplifying their development.
%%   \item \textbf{Common Text Similarity (CTS)}
%%   Text similarity is a common information retrieval technique.
%%   CTS selects lines of a log which are
%%   most similar to the lines present in manually supplied example chunks.
%%   As a common information retrieval technique, our text similarity
%%   approach stands for the machine learning approaches identified in
%%   the literature survey.
%%   \item \textbf{Keyword Search (KWS)}
%%   KWS finds fitting passages by searching the whole
%%   text of a build log for
%%   the occurrence of specific trigger words.
%%   Keyword Search was explicitly mentioned by several articles in the
%%   literature survey.
%% \end{itemize}

@@

To answer this question, in the third step  of \Cref{fig:overview},
we conduct an empirical study assessing the performance
of these chunk retrieval techniques in
real-world projects under a variety of conditions.
Our study is based on the \emph{LogChunks} data
set~\cite{brandt2020logchunks}, which encompasses build logs from
80 popular open-source projects and a broad range of different
build tools and programming languages. Our results show that there is no technique that in general outperforms the others. However, 
% TODO 1-2 sentences about results, inclduing some accuracy measures

>>>>

%% \begin{itemize}
%%   \item \textbf{(referred to as PBE)}
%%   Based on manually supplied example pairs of build logs and chunks,
%%   PBE automatically synthesizes
%%   a regular expression extracting the given chunks within the build
%% logs.
%%   % these second sentences about what the techniques stand for could
%%   % also be merged to a paragraph after the itemize
%%   PBE mimics regular expressions and parsers while
%%   simplifying their development.
%%   \item \textbf{Common Text Similarity (CTS)}
%%   Text similarity is a common information retrieval technique.
%%   CTS selects lines of a log which are
%%   most similar to the lines present in manually supplied example
%% chunks.
%%   As a common information retrieval technique, our text similarity
%%   approach stands for the machine learning approaches identified in
%%   the literature survey.
%%   \item \textbf{Keyword Search (KWS)}
%%   KWS finds fitting passages by searching the whole
%%   text of a build log for
%%   the occurrence of specific trigger words.
%%   Keyword Search was explicitly mentioned by several articles in the
%%   literature survey.
%% \end{itemize}

@@

To answer this question, in the third step  of \Cref{fig:overview},
we conduct an empirical study assessing the performance
of these chunk retrieval techniques in
real-world projects under a variety of conditions.
Our study is based on the \emph{LogChunks} data
set~\cite{brandt2020logchunks}, which encompasses 797 build logs from
80 popular open-source projects and a broad range of different
build tools and programming languages.
Our results show that there is no technique that in general outperforms
the others.
However,
% TODO 1-2 sentences about results, inclduing some accuracy measures
